\documentclass[a4paper,10pt]{article}

\usepackage[a4paper,margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}
\titlespacing*{\section}{0pt}{4pt}{2pt}

\begin{document}

\begin{center}
{\Large \textbf{Abiya Mariyam Alex}}\\
Vadakkadathu House, Muttom P.O, Thumpamon, Pathanamthitta\\
+91 9037984679 \;|\; abiyama329@gmail.com\\
\href{https://github.com/iabiya}{github.com/iabiya} \;|\;
\href{https://linkedin.com/in/abiya-mariyam-alex-229b2b29a}{LinkedIn}
\end{center}

\hrule
\vspace{0.1cm}

\section*{Professional Summary}
Recent B.Tech graduate in Computer Science and
Engineering with a specialization in IoT, Cybersecurity, and
Blockchain. Passionate about technology and eager to
leverage my technical skills while gaining practical
industry experience and contributing to organizational
growth.

\section*{Education}

\textbf{B.Tech in Computer Science and Engineering (IoT, Cyber Security and Blockchain)}\\
Providence College of Engineering and School of Business, Chengannur \hfill 2022--2026\\
APJ Abdul Kalam Technological University\\ 
CGPA: 7.93 (First Class)\

\vspace{0.05cm}

\textbf{Higher Secondary Education (Bio-Maths)}\\
St. John's School, Thumpamon (CBSE) \hfill 2021\\
Percentage: 80.2\% (Distinction)

\vspace{0.05cm}

\textbf{Secondary Education}\\
St. John's School, Thumpamon (CBSE) \hfill 2019\\
Percentage: 83.4\% (Distinction)

\section*{Technical Skills}

\begin{itemize}
\item Programming Languages: Python, Java, C
\item Database: MySQL
\item Operating Systems: Windows
\item Areas of Interest: Computer Science, AI, IoT, Cyber Security, Blockchain
\end{itemize}

\section*{Projects}

\textbf{AI Cricket Coach Using YOLOv8}
\begin{itemize}
\item Developed an AI-powered Cricket Coach using YOLOv8 for real-time cricket shot detection and classification.
\item Trained and optimized models on a dataset of 8,000+ annotated cricket batting images.
\item Integrated XGBoost Regression for performance scoring and batting technique evaluation.
\item Built an Android application with Flask backend to deliver instant shot analysis and voice-based feedback.
\end{itemize}

\textbf{IoT Based Wild Animal Intrusion Detection Using Raspberry Pi 5}
\begin{itemize}
\item Developed an IoT-based wildlife intrusion detection system using Raspberry Pi 5, ESP32, and TensorFlow Lite.
\item Built a machine learning model for real-time detection of wild animals from live video streams.
\item Implemented automated SMS alerts and deterrence mechanisms using lights and buzzers.
\item Created an Android application for remote monitoring and device control.
\end{itemize}

\section*{Internships}

\textbf{Flutter Development Internship} \hfill Jul 2024
\begin{itemize}
\item Developed Android applications using Flutter and Android Studio.
\end{itemize}

\textbf{Cyber Forensics Internship} \hfill Jan 2024
\begin{itemize}
\item Gained practical exposure to Disk, Mobile, and SIM Forensics.
\end{itemize}

\section*{Certifications}
\begin{itemize}
\item Cloud Computing (NPTEL) \hfill july-oct 2024
\item Introduction to Industry 4.0 and Industrial Internet of Things (NPTEL) \hfill jan-apr 2025
\item Google Cloud Career Practitioners Learning Path \hfill 2022
\end{itemize}

\section*{Workshops}
\begin{itemize}
\item A workshop on IoT and Embedded System Integration
by IIT Palakkad Technology IHub Foundation
\item A workshop on Latex for Beginners by providence FOSS
CELL
\item Completion of Cloud Engineer Learning Path Track in
Google Cloud Career Practitioners
\item A workshop on Ethical Hacking
\item Advanced workshop on Python
\end{itemize}

\section*{Languages}
\begin{itemize}
\item Malayalam (Native)
\item English (Professional Proficiency)
\item Hindi (Intermediate)
\end{itemize}

\end{document}